---
title: "Exam #2"
author: "Braden Holt"
date: "6/26/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#setwd
setwd("C:/Users/Braden/Documents/Data Science/Exam2/exam2")

# load packages
library(tidyverse)
library(rio)
library(stargazer)
library(data.table)
library(labelled)
library(WDI)


```

## Questions
1. Clear Environment
```{r, echo = TRUE}
rm(list=ls(all = TRUE))
```

2. Load Data 
```{r, echo = TRUE}
inequality_data <- import("inequality.xlsx")
```

3. This is a cross sectional dataset because it captures a single observation for each variable.
```{r, echo = TRUE}
cross.sectional <- inequality_data$year != 2015
print(cross.sectional)
```

6. It is better to have a lower inequality score because the more unequal country of the three, Brazil, has a higher score.
```{r, echo = TRUE}
inequality_gini_denmark <- subset(inequality_data, country == 'Denmark', select = inequality_gini)
inequality_gini_sweden <- subset(inequality_data, country == 'Sweden', select = inequality_gini)
inequality_gini_brazil <- subset(inequality_data, country == 'Brazil', select = inequality_gini)
```

10. Mean inequality_gini score is 36.81375
```{r, echo = TRUE}
mean(na.omit(inequality_data$inequality_gini))
```


11. If Else Commands and Dummy Variables
```{r, message =  FALSE, warning = FALSE}
inequality_data$high_inequality = NA
inequality_data$low_inequality = NA

inequality_data$high_inequality <-
  if(inequality_data$inequality_gini > 36.81375){
    inequaity_data$high_inequality = 1
  } else if (inequality_data$inequality_gini < 36.81375) {
    inequality_data$high_inequality = 0
  }

inequality_data$low_inequality <- 
  if(inequality_data$inequality_gini < 36.81375){
    inequality_data$low_inequality = 1
  } else if (inequality_data$inequality_gini < 36.81375) {
    inequality_data$low_inequality = 0
  }
```


12. For Loop
```{r, echo = TRUE}
x <- c("The World Bank", "African Development Bank", "Bill and Melinda Gates Foundation")

for(i in x){
  print(x)
}
```


14. Import WDI Data

```{r, echo = TRUE}
gdp_per_cap <- WDI(country = 'all',
                       indicator = c('NY.GDP.PCAP.CD'),
                       start = 2015,
                       end = 2015, 
                       cache = NULL,
                       extra = FALSE)
```

16. Rename Variables
```{r, echo = TRUE}
setnames(gdp_per_cap, "NY.GDP.PCAP.CD", "GDP Per Capita")
```

17. Merge Data
```{r, echo = FALSE}
merged_df <- left_join(inequality_data, gdp_per_cap, keep = FALSE)
```


18. Remove Missing Data
```{r, echo = TRUE}
merged_df<- merged_df %>% 
  dplyr::filter(!(inequality_gini == "NA"))
```

19. Keep Inequality Scores > 30
```{r, echo = TRUE}
data_greater_30 <- 
  merged_df %>% 
  dplyr::filter(inequality_gini > 30)

```

20. Sum of 'ai'
```{r, echo = TRUE}
sum(grep("ai", data_greater_30))
```


21. Apply Function
```{r, echo = TRUE}
sapply(data_greater_30$inequality_gini, sum)

```

22. Label
```{r}
var_label(merged_df) <- list('country' = "Country",
                             'iso2c' = "ISO2C Country Code",
                             'inequality_gini' = "Inequality Score",
                             'year' = "Year",
                             'high_inequality' = "High Inequality",
                             'low_inequality' = "Low Inequality",
                             'GDP Per Capita' = "GDP Per Capita")
```